Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2021-01-05 awipev-CO2.Rmd
Difference fco2_fb - fco2_fb_insi_temp

```{r pco2 to fco2, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- d_all %>%
  dplyr::mutate(
    fco2_fb = seacarb::p2fCO2(
      pCO2 = pco2_fb,
      T = temp_fb,
      Patm = 1,
      P = 0),
    fco2_fb_insi_temp = seacarb::fCO2insi(
      fCO2lab = fco2_fb,
      Tlab = temp_fb,
      SST = temp_insitu_11m),
    .after = pco2_fb
)
```

We first calculate fCO2 from pCO2 and then express fCO2 at in situ temperature. Ideally, this should be done with SST as the goal is to estimate air-sea CO2 fluxes. I therefroe use the in situ temperature at 11 m and we will need to speculate on stratitication.

>>>>

```{r pco2 to fco2, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- d_all %>%
  dplyr::mutate(
    fco2_fb = seacarb::p2fCO2(
      pCO2 = pco2_fb,
      T = temp_fb,
      Patm = 1,
      P = 0),
    fco2_fb_insi_temp = seacarb::fCO2insi(
      fCO2lab = fco2_fb,
      Tlab = temp_fb,
      SST = temp_insitu_11m),
    .after = pco2_fb
)

set.caption("Difference fco2_fb - fco2_fb_insi_temp")
pander(summary(d_all$fco2_fb - d_all$fco2_fb_insi_temp))
```

We first calculate fCO2 from pCO2 and then express fCO2 at in situ temperature. Ideally, this should be done with SST as the goal is to estimate air-sea CO2 fluxes. I therefore use the in situ temperature at 11 m and we will need to speculate on stratification.
